Response to the defense feedback

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

\section{Side-channel Attacks}
While there are many kinds of side-channel attacks, we focus on address-based side-channel attacks in this dissertation.
Address-based side-channel attacks happen when a program accesses different memory locations as it processes different secrets. In modern computer systems, an attacker may share hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}. An attacker can probe the shared hardware resource to infer the memory accesses of the victim. While the root cause of the attack is the same, there are many approaches, and an attacker can exploit side-channel leakage sites in different methods to retrieve the information at different granularities.

@@

\subsubsection*{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch. Researchers~\cite{bernstein2008chacha,langley2016chacha20} design and implement new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks. Unfortunately, writing side-channel resistant cryptography code and validating the security property can be tedious and error-prone.  Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which encompasses formal verification methods to design, analyze and implement the cryptography libraries. Formal verification on side-channel leakages starts with a leakage model, which abstracts what an attacker can observe during an attack. After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that observations are independent of the input secrets. The property is an example of \textit{noninterference} or \textit{secure information flow}. Eldib et al.~\cite{eldib2014smt} propose using a SMT solver based method to formally verifying masked implementations. Bayrak et al.~\cite{bayrak2013sleuth} verify power-based side-channel countermeasures.  However, achieving noninterferecne for real-world software is often impractical and researchers also seek to compromised solutions such as quantitative information flow (see Section~\ref{sec:qif}).

>>>>

\section{Side-channel Attacks}
While there are many kinds of side-channel attacks, we focus on address-based side-channel attacks in this dissertation.
Address-based side-channel attacks happen when a program accesses different memory locations as it processes different secrets. In modern computer systems, an attacker may share hardware resources (e.g., Cache, TLB, and DRAM) with the victim~\cite{ge2018survey,szefer2019survey}. An attacker can probe the shared hardware resource to infer the memory accesses of the victim. While the root cause of the attack is the same, an attacker can exploit side-channel leakage sites in different methods to retrieve the information at different granularities.

@@

\subsubsection*{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch. Researchers~\cite{bernstein2008chacha,langley2016chacha20} design and implement new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks. Unfortunately, writing side-channel resistant cryptography code and validating the security property can be tedious and error-prone.  Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which encompasses formal verification methods to design, analyze and implement the cryptography libraries. Formal verification on side-channel leakages starts with a leakage model, which abstracts what an attacker can observe during an attack. After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that observations are independent of the input secrets. The property is an example of \textit{noninterference} or \textit{secure information flow}. Eldib et al.~\cite{eldib2014smt} propose using a SMT solver based method to formally verifying masked implementations. Bayrak et al.~\cite{bayrak2013sleuth} verify power-based side-channel countermeasures by transferring the verification problem into a set of Boolean satisfiability problems. However, achieving noninterferecne for real-world software is often impractical and researchers also seek to compromised solutions such as quantitative information flow (see Section~\ref{sec:qif}).
